\sysfull

### 2018-08-07 paper/asplos19/intro.tex
Intro revised

\item[C2] \emph{Dynamic Memory Consistency Handling:} merging static tasks on the fly rises  the need for dynamic memory consistency handling. This leads to the second challenge: how to dynamically detect inter-coalesced-task data dependencies and ensure efficient protection against power interrupts? \sys addresses this challenge by relying on its novel \emph{Virtual Memory Manager}(VMM). The VMM performs real-time dependency tracking to enable protection on a task transition. Individual variables tracking, however, slows down a system dramatically. Therefore, the VMM keeps memory consistent through \emph{privatizing pages} and optimizes optimize bulk shared-data transfer through Direct Memory Access (DMA).

@@

The rest of this paper is organized as follows. Section~\ref{sec:background} provides background on intermittent computing.
Section~\ref{sec:systemdescription} illustrates an overview of \sys. Section~\ref{sec:task_adaptation} describes \sys's task adaptation mechanism. The the prower interrupt immune virtual memory manager is explained in Section~\ref{sec:memory_virtulaization}. Implementation details of \sys are given in Section~\ref{sec:implementation}. Sections~\ref{sec:methodology} and~\ref{sec:evaluation} describe \sys's evaluation methodology and results, respectively. Section~\ref{sec:related_work} positions \sys in the context of related work and Section~\ref{sec:conclusions} concludes our work.

>>>>

\item[C2] \emph{Dynamic Memory Consistency Handling:} merging static tasks on the fly rises  the need for dynamic memory consistency handling. This leads to the second challenge: how to dynamically detect inter-coalesced-task data dependencies and ensure efficient protection against power interrupts? \sys addresses this challenge by relying on its novel \emph{Virtual Memory Manager} (VMM). The VMM performs real-time dependency tracking to enable protection on a task transition. Individual variables tracking, however, slows down a system dramatically. Therefore, the VMM keeps memory consistent through \emph{privatizing pages} and optimizes optimize bulk shared-data transfer through Direct Memory Access (DMA).

@@

The rest of this paper is organized as follows. Section~\ref{sec:background} provides background on intermittent computing.
Section~\ref{sec:systemdescription} illustrates an overview of \sys. Section~\ref{sec:task_adaptation} describes \sys's task adaptation mechanism. The power interrupt immune virtual memory manager is explained in Section~\ref{sec:memory_virtulaization}. Implementation details of \sys are given in Section~\ref{sec:implementation}. Sections~\ref{sec:methodology} and~\ref{sec:evaluation} describe \sys's evaluation methodology and results, respectively. Section~\ref{sec:related_work} positions \sys in the context of related work and Section~\ref{sec:conclusions} concludes our work.
